Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-07 reports/revision_letter.Rmd
Small changes to revision letter

3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
We have included all of this information in the supplementary file.

@@

1. (Not sure what to address)
2. xyz
3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.

@@

\WorkInProgress
todo{include study design in the forest plots?}

>>>>

1. \todo{I don't really want to add this - I think tables of counts are dumb. Thoughts?}
2. \todo{Yes, we should not have used the term "cases". Clear this up}
3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
We have included all of this information in the supplementary file.

@@

1. \todo{Argue not subjective (pre-specified, objective), and we say in limitations that others might choose other options}
2. \todo{Agree - we pre-specified our approaching thinking that it balanced the need to be conservative with the need to be inclusive. But, many effects fail this (fairly low) bar. Add more on this to the discussion.}
3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.

@@

\WorkInProgress
\todo{include study design in the forest plots?}
